### 2024-07-30 machine-learning.qmd
20240730 - parallelization

```{r}
library("LongituRF")
library("missForest")
library("powerjoin")
library("tidyverse")
```

@@

```{r}
seasonalData_subset_imp <- missForest::missForest(seasonalData_subset %>% data.frame)
```

>>>>

```{r}
library("LongituRF")
library("doParallel")
library("missForest")
library("powerjoin")
library("tidyverse")
```

@@

```{r}
num_cores <- detectCores()
num_cores

registerDoParallel(cores = num_cores)

seasonalData_subset_imp <- missForest::missForest(
  seasonalData_subset %>% data.frame,
  verbose = TRUE,
  mtry = 100,
  parallelize = "variables")
```
